Leadership across cultures and contexts: an exploratory analysis

### 2020-06-22 leadership_across_cultures_contexts.Rmd
Minor change in discussion

There was substantial cross-cultural variation in evidence for most dimensions of leadership: of our `r length(all_study_vars)` dimensions of leadership, `r sum(df_compare2$Estimate < 0.5)` had evidence in less than 50% of our `r nrow(leader_cult)` cultures (Figures \@ref(fig:varsupport) and \@ref(fig:varsupportcb)). There was *systematic* variation in `r vary_n` leadership dimensions by group context, subsistence strategy, continental region, and/or leader sex, factors for which we had complete data for all text records.

>>>>

There was substantial cross-cultural variation in evidence for most leadership dimensions: `r sum(df_compare2$Estimate < 0.5)` of  `r length(all_study_vars)` leadership dimensions had evidence in less than 50% cultures (Figures \@ref(fig:varsupport) and \@ref(fig:varsupportcb)). There was *systematic* variation in `r vary_n` leadership dimensions by group context, subsistence strategy, continental region, and/or leader sex, factors for which we had complete data for all text records.
